---
title: "VALIDATION BE ESAS update feb 2024"
author: "Nicolas Vanermen (INBO)"
date: "23/02/2023"
output:
  html_document:
   df_print: kable
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 100)
```

```{r, include=FALSE}
library(knitr)
library(leaflet)
library(tidyverse)
library(kableExtra)
library(ggplot2)

pathway <- "C:/Users/nicolas_vanermen/Desktop/DATA INVOER/CODING/ICES vocabs and columns/"
filenames_VOCABS <- list.files(pathway, pattern = "*.csv", full.names = TRUE)

for (i in 1:length(filenames_VOCABS)) 
{ split <- str_remove(filenames_VOCABS[i], pattern = pathway)
  name <- str_remove(split, pattern = ".csv")
  file <- read.csv(filenames_VOCABS[i])
  assign(x = name, value = file) }

setwd("C:/Users/nicolas_vanermen/Desktop/DATA INVOER/2023/UPDATES")
CAMPAIGNS <- read.csv("CAMPAIGNS_BE_ICES_update_feb_2024.csv")
SAMPLES <- read.csv("SAMPLES_BE_ICES_update_feb_2024.csv")
POSITIONS <- read.csv("POSITIONS_BE_ICES_update_feb_2024.csv")
OBSERVATIONS <- read.csv("OBSERVATIONS_BE_ICES_update_feb_2024.csv")

# setwd("C:/Users/nicolas_vanermen/Desktop/DATA INVOER/2021/CONVERSION ESAS")
# CAMPAIGNS <- read.csv("CAMPAIGNS_BE_ICES_2022.csv")
# SAMPLES <- read.csv("SAMPLES_BE_ICES_2022.csv")
# POSITIONS <- read.csv("POSITIONS_BE_ICES_2022.csv")
# OBSERVATIONS <- read.csv("OBSERVATIONS_BE_ICES_2022.csv")

# #introduce errors in CAMPAIGNS
# CAMPAIGNS <- rbind(CAMPAIGNS, CAMPAIGNS[1,])
# colnames(CAMPAIGNS)[1] <- "CampaingID"
# CAMPAIGNS[1:5,]$DataAccess <- NA
# CAMPAIGNS[2,]$StartDate <- "18/02/2000"
# CAMPAIGNS[4,]$EndDate <- "18 februari 2000"
#
# #introduce errors in SAMPLES
# SAMPLES <- rbind(SAMPLES, SAMPLES[1,])
# SAMPLES$CampaignID[1] <- 11001028
# colnames(SAMPLES)[1] <- "SamplesID"
# SAMPLES[2,]$Date <- "18/02/2000"
# SAMPLES[5,]$PlatformCode <- NA
# SAMPLES[4,]$PlatformCode <- "blabla"
# SAMPLES[5,]$PlatformClass <- NA
# SAMPLES[4,]$PlatformClass <- "blabla"
# SAMPLES[1:3,]$TransectWidth <- NA
# SAMPLES[4:6,]$SamplingMethod <- NA
# SAMPLES[5:7,]$TargetTaxa <- NA
# SAMPLES[5,]$UseOfBinoculars <- 10

# #introduce errors in POSITIONS
# POSITIONS <- rbind(POSITIONS, POSITIONS[1,])
# POSITIONS$SampleID[1] <- 11201028
# colnames(POSITIONS)[1] <- "PositionssID"
# POSITIONS[2,]$Time <- "1111:11"
# POSITIONS[5,]$Latitude <- NA
# POSITIONS[4:100,]$Longitude <- 0
# POSITIONS[5,]$Distance <- NA
# POSITIONS[4,]$Area <- 0
# POSITIONS[1:3,]$WindForce <- 15
# POSITIONS[4:6,]$Visibility <- 11
# POSITIONS[5:7,]$Glare <- "claire"
# POSITIONS[5,]$IceCover <- 110

# #introduce errors in OBSERVATIONS
# OBSERVATIONS[5,]$SpeciesCode <- 6200
```
<div style="margin-top:75px;">

#  NUMBER OF RECORDS

CAMPAIGNS contains `r nrow(CAMPAIGNS)` records\
SAMPLES contains `r nrow(SAMPLES)` records\
POSITIONS contains `r nrow(POSITIONS)` records\
OBSERVATIONS contains `r nrow(OBSERVATIONS)` records\

<div style="margin-top:75px;">

#  CHECK COLUMN NAMES

colnames CAMPAIGNS: `r ifelse(sum(colnames(CAMPAIGNS)==CAMPAIGNS_column_names)==ncol(CAMPAIGNS), TRUE, FALSE)`\
colnames SAMPLES: `r ifelse(sum(colnames(SAMPLES)==SAMPLES_column_names)==ncol(SAMPLES), TRUE, FALSE)`\
colnames POSITIONS: `r ifelse(sum(colnames(POSITIONS)==POSITIONS_column_names)==ncol(POSITIONS), TRUE, FALSE)`\
colnames OBSERVATIONS: `r ifelse(sum(colnames(OBSERVATIONS)==OBSERVATIONS_column_names)==ncol(OBSERVATIONS), TRUE, FALSE)`\

<div style="margin-top:75px;">

#  VALIDATE CAMPAIGNS 
###  CampaignID *

No missing values: `r sum(is.na(CAMPAIGNS$CampaignID))==0`\
Unique identifier: `r length(unique(CAMPAIGNS$CampaignID))==nrow(CAMPAIGNS)`

<div style="margin-top:35px;">

###  DataAccess *

No missing values: `r sum(is.na(CAMPAIGNS$DataAccess))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_DataAccess <- as.data.frame(table(CAMPAIGNS$DataAccess))
names(table_DataAccess)[1] <- "DataAccess"
table_DataAccess %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  StartDate

Formatted as YYYY-MM-DD: 
`r  nrow(CAMPAIGNS[grepl("[0-9]{4}-[0-9]{2}-[0-9]{2}",CAMPAIGNS$StartDate),]) ==
    nrow(CAMPAIGNS[!is.na(CAMPAIGNS$StartDate),])`

<div style="margin-top:35px;">

###  EndDate

Formatted as YYYY-MM-DD: 
`r  nrow(CAMPAIGNS[grepl("[0-9]{4}-[0-9]{2}-[0-9]{2}",CAMPAIGNS$EndDate),]) ==
    nrow(CAMPAIGNS[!is.na(CAMPAIGNS$EndDate),])`

<div style="margin-top:75px;">

#  VALIDATE SAMPLES 
###  CampaignID *

No missing values: `r sum(is.na(SAMPLES$CampaignID))==0`\
Link to CAMPAIGNS:
`r nrow(SAMPLES[SAMPLES$CampaignID %in% CAMPAIGNS$CampaignID,])==nrow(SAMPLES)`

<div style="margin-top:35px;">

###  SampleID *

No missing values: `r sum(is.na(SAMPLES$SampleID))==0`\
Unique identifier: `r length(unique(SAMPLES$SampleID))==nrow(SAMPLES)`

<div style="margin-top:35px;">

###  Date *
No missing values: `r sum(is.na(SAMPLES$Date))==0`\
Formatted as YYYY-MM-DD: 
`r  nrow(SAMPLES[grepl("[0-9]{4}-[0-9]{2}-[0-9]{2}",SAMPLES$Date),]) ==
    nrow(SAMPLES)`

<div style="margin-top:35px;">

###  PlatformCode *

No missing values: `r sum(is.na(SAMPLES$PlatformCode))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_PlatformCode <- merge(
  as.data.frame(table(SAMPLES$PlatformCode)), 
  SHIPC[,c("Key","Description")], 
  by.x="Var1", by.y="Key", all.x=T)
names(table_PlatformCode)[1] <- "PlatformCode"
table_PlatformCode[,c(1,3,2)]  %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  PlatformClass *

No missing values: `r sum(is.na(SAMPLES$PlatformClass))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_PlatformClass <- merge(
  as.data.frame(table(SAMPLES$PlatformClass)),
  PlatformClass[,c("Key","Description")], 
  by.x="Var1", by.y="Key", all.x=T)
names(table_PlatformClass)[1] <- "PlatformClass"
table_PlatformClass[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  PlatformSide

Missing values: `r round(100*sum(is.na(SAMPLES$PlatformSide))/nrow(SAMPLES), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(SAMPLES$PlatformSide))>0)
  {
  table_PlatformSide <- as.data.frame(table(SAMPLES$PlatformSide))
  names(table_PlatformSide)[1] <- "table_PlatformSide"
  table_PlatformSide %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  PlatformHeight

Missing values: `r round(100*sum(is.na(SAMPLES$PlatformHeight))/nrow(SAMPLES), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(SAMPLES$PlatformHeight))>0) 
  {
  table_PlatformHeight <- as.data.frame(table(SAMPLES$PlatformHeight))
  names(table_PlatformHeight)[1] <- "table_PlatformHeight"
  table_PlatformHeight %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  TransectWidth *

No missing values: `r sum(is.na(SAMPLES$TransectWidth))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_TransectWidth <- as.data.frame(table(SAMPLES$TransectWidth))
names(table_TransectWidth)[1] <- "TransectWidth"
table_TransectWidth %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  SamplingMethod *

No missing values: `r sum(is.na(SAMPLES$SamplingMethod))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_SamplingMethod <- merge(
  as.data.frame(table(SAMPLES$SamplingMethod)),
  BD_CountMethod[,c("Key","Description")], 
  by.x="Var1", by.y="Key", all.x=T)
names(table_SamplingMethod)[1] <- "SamplingMethod"
table_SamplingMethod[,c(1,3,2)]  %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  PrimarySampling

Missing values: `r round(100*sum(is.na(SAMPLES$PrimarySampling))/nrow(SAMPLES), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(SAMPLES$PrimarySampling))>0) 
  {
  table_PrimarySampling <- as.data.frame(table(SAMPLES$PrimarySampling))
  names(table_PrimarySampling)[1] <- "PrimarySampling"
  table_PrimarySampling %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  TargetTaxa *

No missing values: `r sum(is.na(SAMPLES$TargetTaxa))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_TargetTaxa <- merge(
  as.data.frame(table(SAMPLES$TargetTaxa)),
  TargetTaxa[,c("Key","Description")], 
  by.x="Var1", by.y="Key", all.x=T)
names(table_TargetTaxa)[1] <- "TargetTaxa"
table_TargetTaxa[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  DistanceBins

Missing values: `r round(100*sum(is.na(SAMPLES$DistanceBins))/nrow(SAMPLES), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(SAMPLES$DistanceBins))>0) 
  {
  table_DistanceBins <- as.data.frame(table(SAMPLES$DistanceBins))
  names(table_DistanceBins)[1] <- "DistanceBins"
  table_DistanceBins %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  UseOfBinoculars

Missing values: `r round(100*sum(is.na(SAMPLES$UseOfBinoculars))/nrow(SAMPLES), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(SAMPLES$UseOfBinoculars))>0) 
  {
  table_UseOfBinoculars <- merge(
    as.data.frame(table(SAMPLES$UseOfBinoculars)), 
    UseOfBinoculars[,c("Key","Description")], 
    by.x="Var1", by.y="Key", all.x=T)
  names(table_UseOfBinoculars)[1] <- "UseOfBinoculars"
  table_UseOfBinoculars[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  NumberOfObservers

Missing values: `r round(100*sum(is.na(SAMPLES$NumberOfObservers))/nrow(SAMPLES), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(SAMPLES$NumberOfObservers))>0)
  {
  table_NumberOfObservers <- as.data.frame(table(SAMPLES$NumberOfObservers))
  names(table_NumberOfObservers)[1] <- "NumberOfObservers"
  table_NumberOfObservers %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:75px;">

#  VALIDATE POSITIONS
###  SampleID *

No missing values: `r sum(is.na(POSITIONS$SampleID))==0`\
Link to SAMPLES: `r nrow(POSITIONS[POSITIONS$SampleID %in% SAMPLES$SampleID,])==nrow(POSITIONS)`

<div style="margin-top:35px;">

###  PositionID *

No missing values: `r sum(is.na(POSITIONS$PositionID))==0`\
Unique identifier: `r length(unique(POSITIONS$PositionID))==nrow(POSITIONS)`

<div style="margin-top:35px;">

###  Time *
No missing values: `r sum(is.na(POSITIONS$Time))==0`\
Formatted as hh:mm:ss: `r  nrow(POSITIONS[grepl("[0-9]{2}:[0-9]{2}:[0-9]{2}",POSITIONS$Time),]) == nrow(POSITIONS)`

<div style="margin-top:35px;">

###  Latitude / Longitude *

No missing values: `r sum(is.na(POSITIONS[,c("Latitude","Longitude")]))==0`

```{r, echo=FALSE, error=TRUE, comment=""}
summary(POSITIONS[,c("Latitude","Longitude")])
Map <- leaflet(POSITIONS) %>%
  addTiles() %>%
  addCircleMarkers(lng = POSITIONS$Longitude,
                   lat = POSITIONS$Latitude, radius = 1, fillOpacity = 1, stroke = FALSE)
Map
```

<div style="margin-top:35px;">

###  Distance *

No missing values: `r sum(is.na(POSITIONS$Distance))==0`\
No zeros : `r sum(POSITIONS$Distance%in%c(0))==0`

<div style="margin-top:35px;">

###  Area *

No missing values: `r sum(is.na(POSITIONS$Area))==0`\
No zeros : `r sum(POSITIONS$Area%in%c(0))==0`

<div style="margin-top:35px;">

**Distance / Area summaries:**
```{r, error=TRUE, comment=""}
summary(POSITIONS[,c("Distance","Area")])
POS <- merge(POSITIONS, SAMPLES[,c("SampleID","TransectWidth")])
POS <- POS %>% mutate(test = (Distance*TransectWidth/1000)/Area)
summary(POS$test)
```

<div style="margin-top:35px;">

###  WindForce

Missing values: `r round(100*sum(is.na(POSITIONS$WindForce))/nrow(POSITIONS), digits=1)` %

<div style="margin-top:25px;">

```{r, echo=FALSE, error=TRUE, comment=">"}
if(sum(!is.na(POSITIONS$WindForce))>0)
  {
  ggplot(POSITIONS, aes(as.factor(WindForce))) + geom_bar()
  }
```

<div style="margin-top:35px;">

###  Visibility

Missing values: `r round(100*sum(is.na(POSITIONS$Visibility))/nrow(POSITIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(POSITIONS$Visibility))>0)
  {
  table_Visibility <- merge(
    as.data.frame(table(POSITIONS$Visibility)), 
    Visibility[,c("Key","Description")], 
    by.x="Var1", by.y="Key", all.x=T)
  names(table_Visibility)[1] <- "Visibility"
  table_Visibility[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  Glare

Missing values: `r round(100*sum(is.na(POSITIONS$Glare))/nrow(POSITIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(POSITIONS$Glare))>0)
  {
  table_Glare <- merge(
    as.data.frame(table(POSITIONS$Glare)), 
    Glare[,c("Key","Description")],
    by.x="Var1", by.y="Key", all.x=T)
  names(table_Glare)[1] <- "Glare"
  table_Glare[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  SunAngle
#### (expressed in degrees)
Missing values: `r round(100*sum(is.na(POSITIONS$SunAngle))/nrow(POSITIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(POSITIONS$SunAngle))>0)
  {
  summary(POSITIONS$SunAngle)
  }
```

<div style="margin-top:35px;">

###  CloudCover
#### (expressed in octas)
Missing values: `r round(100*sum(is.na(POSITIONS$CloudCover))/nrow(POSITIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(POSITIONS$CloudCover))>0)
  {
  summary(POSITIONS$CloudCover)
  }
```

<div style="margin-top:35px;">

###  Precipitation

Missing values: `r round(100*sum(is.na(POSITIONS$Precipitation))/nrow(POSITIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(POSITIONS$Precipitation))>0)
  {
  table_Precipitation <- merge(
    as.data.frame(table(POSITIONS$Precipitation)), 
    Precipitation[,c("Key","Description")],
    by.x="Var1", by.y="Key", all.x=T)
  names(table_Precipitation)[1] <- "Precipitation"
  table_Precipitation[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  IceCover
#### (expressed in percentage)
Missing values: `r round(100*sum(is.na(POSITIONS$IceCover))/nrow(POSITIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(POSITIONS$IceCover))>0)
  {
  summary(POSITIONS$IceCover)
  }
```

<div style="margin-top:35px;">

###  ObservationConditions

Missing values: `r round(100*sum(is.na(POSITIONS$ObservationConditions))/nrow(POSITIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}

if(sum(!is.na(POSITIONS$ObservationConditions))>0)
  {
  table_ObservationConditions <- merge(
    as.data.frame(table(POSITIONS$ObservationConditions)),
    Sightability[,c("Key","Description")], 
    by.x="Var1", by.y="Key", all.x=T)
  names(table_ObservationConditions)[1] <- "ObservationConditions"
  table_ObservationConditions[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:75px;">

#  VALIDATE OBSERVATIONS
###  PositionID *

No missing values: `r sum(is.na(OBSERVATIONS$PositionID))==0`\
Link to SAMPLES: `r nrow(OBSERVATIONS[OBSERVATIONS$PositionID %in% POSITIONS$PositionID,])==nrow(OBSERVATIONS)`

<div style="margin-top:35px;">

###  ObservationID *

No missing values: `r sum(is.na(OBSERVATIONS$ObservationID))==0`\
Unique identifier: `r length(unique(OBSERVATIONS$ObservationID))==nrow(OBSERVATIONS)`

<div style="margin-top:35px;">

###  GroupID

```{r, echo=FALSE, error=TRUE, comment=""}
summary(OBSERVATIONS$GroupID)
```

<div style="margin-top:35px;">

###  Transect *

No missing values: `r sum(is.na(OBSERVATIONS$Transect))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_Transect <- as.data.frame(table(OBSERVATIONS$Transect))
names(table_Transect)[1] <- "Transect"
table_Transect %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  SpeciesCodeType *

No missing values: `r sum(is.na(OBSERVATIONS$SpeciesCodeType))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
table_SpeciesCodeType <- as.data.frame(table(OBSERVATIONS$SpeciesCodeType))
names(table_SpeciesCodeType)[1] <- "SpeciesCodeType"
table_SpeciesCodeType %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  Species *

No missing values: `r sum(is.na(OBSERVATIONS$SpeciesCode))==0`\

Species code(s) with no corresponding code in the ESAS species vocabulary: 
```{r, echo=FALSE, error=TRUE, comment=""}
unique(OBSERVATIONS[!(OBSERVATIONS$SpeciesCode %in% Species$esas_code),]$SpeciesCode)
```

<div style="margin-top:35px;">

```{r, echo=FALSE, error=TRUE, comment=""}
species_list <- as.data.frame(table(OBSERVATIONS$SpeciesCode))
species_list <- merge(species_list, Species[,c("esas_code","scientific_name","english_name")], by.x="Var1", by.y="esas_code")
species_list <- species_list %>% 
  arrange(as.integer(as.character(Var1))) %>%
  rename(ESAS_code = Var1)
row.names(species_list) <- NULL
species_list[,c(1,4,3,2)] %>%
  kbl(table.attr = "style='width:75%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  Count *

No missing values: `r sum(is.na(OBSERVATIONS$Count))==0`\

```{r, echo=FALSE, error=TRUE, comment=""}
summary(OBSERVATIONS$Count)
```

<div style="margin-top:35px;">

###  ObservationDistance

Missing values: `r round(100*sum(is.na(OBSERVATIONS$ObservationDistance))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
table_ObservationDistance <- as.data.frame(table(OBSERVATIONS$ObservationDistance, OBSERVATIONS$Transect))
table_ObservationDistance <- table_ObservationDistance %>%
  spread(Var2, Freq) %>%
  rename(ObservationDistance = Var1)
table_ObservationDistance %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
```

<div style="margin-top:35px;">

###  LifeStage

Missing values: `r round(100*sum(is.na(OBSERVATIONS$LifeStage))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$LifeStage))>0)
  {
  table_LifeStage <- as.data.frame(table(OBSERVATIONS$LifeStage))
  names(table_LifeStage)[1] <- "LifeStage"
  table_LifeStage %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  Moult

Missing values: `r round(100*sum(is.na(OBSERVATIONS$Moult))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$Moult))>0)
  {
  table_Moult <- as.data.frame(table(OBSERVATIONS$Moult))
  names(table_Moult)[1] <- "Moult"
  table_Moult %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  Plumage

Missing values: `r round(100*sum(is.na(OBSERVATIONS$Plumage))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$Plumage))>0)
  {
  table_Plumage <- as.data.frame(table(OBSERVATIONS$Plumage))
  names(table_Plumage)[1] <- "Plumage"
  table_Plumage %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  Sex

Missing values: `r round(100*sum(is.na(OBSERVATIONS$Sex))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$Sex))>0)
  {
  table_Sex <- as.data.frame(table(OBSERVATIONS$Sex))
  names(table_Sex)[1] <- "Sex"
  table_Sex %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  TravelDirection

Missing values: `r round(100*sum(is.na(OBSERVATIONS$TravelDirection))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$TravelDirection))>0)
  {
  table_TravelDirection <- as.data.frame(table(OBSERVATIONS$TravelDirection))
  names(table_TravelDirection)[1] <- "TravelDirection"
  table_TravelDirection %>%
  kbl(table.attr = "style='width:30%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  Prey

Missing values: `r round(100*sum(is.na(OBSERVATIONS$Prey))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$Prey))>0)
  {
  table_Prey <- merge(
    as.data.frame(table(OBSERVATIONS$Prey)),
    PreyType[,c("Key", "Description")],
    by.x="Var1", by.y="Key", all.x=T)
  names(table_Prey)[1] <- "Prey"
  table_Prey[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  Association

Missing values: `r round(100*sum(is.na(OBSERVATIONS$Association))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$Association))>0)
  {
  table_Association <- merge(
    as.data.frame(table(OBSERVATIONS$Association)),
    Association[,c("Key", "Description")],
    by.x="Var1", by.y="Key", all.x=T)
  names(table_Association)[1] <- "Association"
  table_Association[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">

###  Behaviour

Missing values: `r round(100*sum(is.na(OBSERVATIONS$Behaviour))/nrow(OBSERVATIONS), digits=1)` %

```{r, echo=FALSE, error=TRUE, comment=""}
if(sum(!is.na(OBSERVATIONS$Behaviour))>0)
  {
  table_Behaviour <- merge(
    as.data.frame(table(OBSERVATIONS$Behaviour)),
    Behaviour[,c("Key", "Description")],
    by.x="Var1", by.y="Key", all.x=T)
  names(table_Behaviour)[1] <- "Behaviour"
  table_Behaviour[,c(1,3,2)] %>%
  kbl(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left", font = 12)
  }
```

<div style="margin-top:35px;">
